Effectful Semantics for Substructural SSA

### 2023-11-14 pldi24/paper.tex
Tap at definitions

\begin{definition}[Binoidal Category] \
  \TODO{this}
\end{definition}

\begin{definition}[Premonoidal Category] \
  \TODO{this}
\end{definition}

@@

\begin{definition}[Strictly Effectful Category] \
  \TODO{this}
\end{definition}

>>>>

\begin{definition}[Binoidal Category] 
  A \textbf{binoidal category} \(\mc{C}\) is a category equipped with a binary
  operation on objects \(\otimes: \mc{C} \times \mc{C} \to \mc{C}\) which is
  independently functorial in each argument (i.e., for each object \(A\), \(A
  \otimes -\) and \(- \otimes A\) are functors).
\end{definition}
Given \(f: \mc{C}(A, B)\), \(g: \mc{C}(A', B')\) in a binoidal category, we
write \(f \ltimes g = f \otimes A';B \otimes g\) and \(f \rtimes g = A \otimes
g;f \otimes B'\); we say \(f\) is \textbf{central} if, for all \(g\), \(f
\ltimes g = f \rtimes g\) and \(g \ltimes f = g \rtimes f\), in which case we
simply write \(f \otimes g\), \(g \otimes f\) respectively.

\begin{definition}[Premonoidal Category] 
  A \textbf{premonoidal category} is a binoidal category with an identity object
  \(I: \mc{C}\) such that
  \begin{itemize}
    \item There exist central natural isomorphisms \(\lambda_A: I \otimes A
    \simeq A\) (the \textbf{left unitor}), \(\rho_A: A \otimes I \simeq A\) (the
    \textbf{right unitor})
    \item There exists a central isomorphism \(\alpha_{A, B, C}: (A \otimes B)
    \otimes C \simeq A \otimes (B \otimes C)\) (the \textbf{associator})
    \item Satisfying the \textbf{pentagon law}: \todo{this}
    \item Satisfying the \textbf{triangle law}: \todo{this}
  \end{itemize}
  We say a premonoidal category is \textbf{symmetric} if it is equipped with a
  central natural isomorphism \(\sigma_{A, B}: A \otimes B \simeq B \otimes A\)
  (the \textbf{symmetry}) satisfying the \textbf{hexagon law} \todo{this}.

  We say a premonoidal category is \textbf{monoidal} if every morphism is
  central.
\end{definition}

@@

% Should we go down this road?
% \begin{definition}[Strictly Effectful Category] \
%   \TODO{this}
% \end{definition}

% \TODO{text}
